The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-05 main.tex
rephrase
empower -> enable

Astronomers often need to compute statistics of quantities evaluated on a
circle, such as sky direction or polarization angle.
A set of circular statistical estimators based on \citet{JammalamadakaSengupta}
are implemented in \package{astropy.stats}.  These functions provide
measurements of the circular mean, variance, and moment.   For all of these
functions, they work with both \texttt{numpy.ndarrays} (assumed to be in
radians) and \texttt{Quantity} objects.  In addition, the subpackage includes
tests for Rayleigh Test, \texttt{vtest}, and a function to compute the maximum
likelihood estimator for the parameters of the von Mises distribution.

@@

\astropy also provides a set of scripts for setting up and configuring
CI services as a \github repository,
\package{astropy/ci-helpers}.\footnote{\url{https://github.com/astropy/ci-helpers}}
These tools aim to empower package maintainers to control their testing setup
and installation process for various CI services through a
set of environment variables.
While the current development is mostly driven by the needs of the \astropy
ecosystem, the actual usage of this package is extremely widespread. The current
tools support configuration for Travis CI and Appveyor CI.

>>>>

Astronomers often need to compute statistics of quantities evaluated on a
circle, such as sky direction or polarization angle.
A set of circular statistical estimators based on \citet{JammalamadakaSengupta}
are implemented in \package{astropy.stats}.  These functions provide
measurements of the circular mean, variance, and moment.   All of these
functions work with both \texttt{numpy.ndarrays} (assumed to be in radians) and
\texttt{Quantity} objects.  In addition, the subpackage includes
tests for Rayleigh Test, \texttt{vtest}, and a function to compute the maximum
likelihood estimator for the parameters of the von Mises distribution.

@@

\astropy also provides a set of scripts for setting up and configuring
CI services as a \github repository,
\package{astropy/ci-helpers}.\footnote{\url{https://github.com/astropy/ci-helpers}}
These tools aim to enable package maintainers to control their testing setup
and installation process for various CI services through a
set of environment variables.
While the current development is mostly driven by the needs of the \astropy
ecosystem, the actual usage of this package is extremely widespread. The current
tools support configuration for Travis CI and Appveyor CI.
